### 2020-01-06 Literature Review/Literature Review - Revised/.history/sections/GameTheory_20200106140400.tex
Updated Game Dynamics

\maketitle

\tableofcontents

\chapter*{Introduction}

The areas of interest regarding Multi Agent Systems fall into two
distinct categories (which have some slight overlap). The first is
denoted as 'Decision Making', though the terms 'Planning' and
'Distributed Control' may sometimes be used as substitutes. It is
important to note that, in my case, I do not include Planning
Formalisation techniques such as PDDL. Instead, I focus on the
particular methods which involve interaction in the world. The second,
I will refer to as 'Multi Agent Dynamics', though sometimes I will
refer to this as 'Stability Analysis'.

\subsection*{Scope}

Both of the aforementioned topics have been applied to all variants of
multi agent systems and have sufficient room for further
exploration. The typical variants of multi agent systems that I will
consider are

\begin{enumerate} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
Coded \end{enumerate}

In the above, 'Game Theoretic Approaches' cover a wide spectrum,
including zero-sum (minimax) games, bayesian games, and many more. The
final category, 'Hard Coded', refers to any approach which does not
fit neatly into any of these categories. The name is chosen since they
often refer to methods which revolve around a series of if-else
statements.

\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}

I will first consider Decision Making as this is most closely related
to the research proposal, before I consider Multi Agent Dynamics,
which has strong implications for Safe and Trusted Multi Agent
Systems.

\subsection*{Objectives}

The aim of the following sections is not to provide an exhaustive list of all work done in the
aforementioned areas. To attempt to do this would be an exercise in futility. Instead, it is to
identify research directions which lie within the broad scope of Multi-Agent Systems (MAS). With
these directions, we may be able to narrow down the remaining literature review and hone in on
particular problems and, in fact, we may find that we address multiple of these over the next four
years (while we, of course add more). As such, the end of each chapter will provide a list of
research directions which I have identified from the preceding review.

\chapter{Decision Making}

Decision making refers to the generalised problem of considering how a multi-agent system should
interact in the world to achieve their goals. This subsumes both the cases where the agents' goals
are aligned (cooperative) or in conflict with one another (competitive).

The following sections will provide an overview of the literature aimed towards coordinating such
systems as followed by interesting sub-fields in each approach which present avenues for research
related to Safe and Trusted AI (STAI). These, of course, are not exhaustive and more will be added
as the review progresses.

\section{Swarms}

Swarm based systems comprise of multiple homogeneous agents which are able to organise themselves
through a formation using a series of simple local interactions with their neighbours
\cite{Couceiro2015}. Whilst the individual agents are generally simplistic, the collective behaviour
may exhibit complex phenomena emulating systems observed in biological organisations such as bee or
ant colonies \cite{Sethi2017}. Hybrid algorithms such as in \cite{Gao2018} show an accelerated
performance in reaching globally optimal solutions in search-based tasks. The advantage of many
swarm algorithms is that they are based on local interactions and so are incredibly scalable
\cite{Rizk2018}.

The reduction of the complexity in interactions between agents also allows for the robots to perform
other calculations on board. In \cite{Pini2011TaskSelection}, Pini et al. leverage this by
considering adaptive task partitioning across swarms. This allows a swarm, in a decentralised
manner, to deliberate whether to partition a task into its sub-tasks or to perform the task in its
whole. As of now (to the best of my knowledge) the problem of partitioning general tasks into its N
sub-tasks is unexplored. This, however, highlights another advantage of swarm systems; they are
readily divided into sub-groups (as in \cite{Zahadat2016DivisionInhibition}) to perform a
divide-et-impera (divide and conquer) approach to solving problems \cite{Pini2011TaskSelection}).

Furthermore, swarm systems may be designed in a leaderless manner and so do not require the use of a
central controller \cite{Couceiro2015}. This presents the advantage that the system can rapidly
adapt to the loss of agents or separation of groups throughout the task. However, the assumptions
made regarding the homogeneity of individual agents and the simplicity of their local interactions
result in significant limitations placed on the complexity of the tasks that swarm systems can
accomplish.

\fr{What are the standard techniques used in swarms? that is, how are swarms and their interactions modelled? how are solutions computed? what kind of algorithms are used in this area? most importantly, does any of these overlap with any of the areas below, for example (PO)MDPs?}

\subsection{Co-evolution and Self-Healing}

Recently, there has been an increased interest in introducing
heterogeneity into the swarm systems to improve their real world
applicability. An example of this which have been shown strong real
world success can be found in
\cite{DucatelleSelf-organizedSwarms}. Here, the authors consider two
swarm teams, referred to as 'foot bots' and 'eye bots' who work in
unison to explore an environment and solve a navigation task.

This area of research is sparsely populated and warrants further
exploration. This is since the use of co-evolutionary teams can
improve the robustness of the swarm optimisation. This is since it
will be possible for a team to automatically determine when robots in
the other team are not exhibiting expected behaviour and ensure that
the other team self corrects. This process is referred to as
'Self-Healing' in \cite{LiuTrust-Aware}. Here, the authors allow a
user to define the goals of a swarm system. From this, a 'trust'
metric can be defined which measures the deviation of each agent from
the expected behaviour. The self-healing process occurs by limiting
communication of all agents with 'untrusted' agents and encouraging
communication with 'trusted' agents. The unison of self-healing with
co-evolution may present the opportunity for heterogenous swarms to
maintain their evolutionary stability, even in the face of
environmental disturbances.

\subsection{Fault Detection}

The above sections have considered the fact that swarm systems are
robust to losses in the group.  However, any MAS system must first be
able to recognise that an agent has undergone some failure.

To this end, Tarapore et al. \cite{Tarapore2019FaultDetection} develop
a robust fault detection approach in which the swarm itself, in a
decentralised manner, is capable of assessing deviation from 'normal'
behaviour, even when the behaviour of the swarm itself is altered
(perhaps by a remote operator). The authors achieve this by requiring
that the agents themselves sense and characterise their own
behaviour. This characterisation is formulated as a binary feature
vector which is then communicated to the agent's neighbours. These
neighbours will reach a consensus over whether the agent should be
treated as faulty based on their collective behaviour. The results
presented in \cite{Tarapore2019FaultDetection} show extremely
promising results and suggest that their method is, in fact, able to
determine faults with high accuracy in the presence of various fault
types (including sensor and actuator failures), although poor
performance is seen in actuation failures in some instances. It should
be noted that this method requires that each robot transmit their
feature vector to the nearest neighbours. In environments where
communication may be severely limited, this may present further
errors. Furthermore, it is unlikely that, when a robot is damaged,
only one of its components will be affected. Therefore, it is
important to determine the effect on performance in the face of
multiple agent failures and in communication losses. This exploration
may open the possibility of improving the state of the art in terms of
failure detection in swarm systems. (Of course, this conclusion is
based off two papers so further review is required).

\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas. As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another. However, this depends essentially on the different modelling assumptions.}

\subsection{Verification}

Both of Alessio's papers \cite{Kouvaros2019FormalSystems, Lomuscio2019ASystems} fit in here but they
require further reading

\subsection{Directions}

From the above consideration of swarms, the following research
directions have been identified which, in my view, concern themselves
with STAI.

\begin{enumerate} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as
expected by the user.

\item Fault Detection in limited communication:
Considering the ability of a swarm to, in a decentralised approach,
consider which robots in the team have failed, even in cases of no
communication or multiple failures.

\fr{The second item looks promising, possibly in combinations with
  techniques from Game Theory and MARL. Let's keep Fault R\&D in
  mind.}

\end{enumerate}

\section{Dec-POMDPs}

The use of POMDPs in multi-agent settings is formalised as
decentralised POMDP (Dec-POMDP) which aims for a team of agents to
maximise a common utility. However, it has been found that determining
the exact solution to Dec-POMDP problems is NEXP \cite{Eker2011} and
so is intractable for all but toy problems. A number of methods have
been presented to attempt to solve Dec-POMDPs. Oliehoek gives a review
of these in \cite{OliehoekDecentralizedPOMDPs}. Most solutions (such
as brute force) are intractable for all but toy problems.

Approximate solutions to Dec-POMDP have been proposed, perhaps most
notable of which is the proposal of MacDec-POMDP \cite{Amato2015} by
Amato et al. Here, macro actions (actions which extend over multiple
time steps) are used, as opposed to low-level actions which are
re-evaluated at each time step. This allows an exact solution to be
found as it does not need to be evaluated at each time step. This
method assumes that, once macro-actions are distributed, the policies
(sequence of state-action pairs) are known. Since this is not the
case, Amato also proposes the use of a Dec-POSMDP
\cite{Amato2017Decision-MakingLearning}, where 'SMDP' refers to
'Semi-Markov Decision Process, in which a high level model is defined
without the underlying Dec-POMDP's actions and observations.

However, this is largely applicable in passive settings where common
payoffs can be determined by an offline planner. They also require a
significant amount of data with which to allow the system to learn the
underlying models and payoff structures. This limits the applicability
of the system when communication is limited and the system is
presented with environments that it has not seen before.  Recent work
in MDPs \cite{Klima2019RobustDomains} has considered learning in the
face of Significant Rare Events (SREs) which the system has not yet
observed. Currently, it is required that a model of such SREs is known
and so it would be interesting to consider the application of
Dec-POMDPs in situations where the SRE model is incomplete or
erroneous and assess the robustness of the Dec-POMDP framework against
such events.

\subsection{Directions}

The area of Dec-POMDPs still requires more review from me, especially for solutions which are not
developed by Amato as he seems to largely dominate the field. Based on this initial review of the
area, a potential direction for research is

\begin{enumerate} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
  SREs which have a limited or erroneous model.

\item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{enumerate}

\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
Also, it might be interesting to understand why swarms scale up better
than MDPs, and in general why the former have better computational
properties than the latter: is it a matter of
``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
some other swarm-like restriction? It might be interesting to combine
the two approaches in order to get the ``best of both worlds''.}

\section{Game Theoretic Approaches}

Game theoretic models are generally the go-to method for understanding
multi-agent systems. As such they fit into all of the categories in
this chapter (except, perhaps, swarms) since Dec-POMDP and MARL
methods have both used game theory to support their frameworks. In
fact, Dec-POMDP is a subset of Partially Observed Stochastic Games
(POSG), in which all agents use the same payoff. \fr{That's an
  interesting remark. It might be worth to check whether we can
  leverage on this and similar observations.} Game theory can,
therefore, be used in an applied capacity to direct task allocation
across heterogenous teams.

\subsection{Market Based Methods}

@@

Whilst there are different variants to autioning, the general
procedure is that an auctioneer who has knowledge of a task (or
multiple tasks) will set up an auction for said task. Agents can then
make bids on these tasks and, once the auction is complete, the
highest bid will win the task. In the specific application to
robotics, a robot's bid will often reflect the costs, suitability or
utility their undertaking the task
\cite{BernardineDias2006Market-basedAnalysis}. This immediately
highlights a few points. The first is that the method is not too
heavily reliant upon a single processor to determine some joint
policy. Tasks are allocated on a case-by-case basis and the utilities
are calculated by the agent themselves. The only centralised process
is the auctioneer's assessment of the winner which then relays this
information back to them. The downside of this is that the system is
heavily reliant upon strong communication channels, without which
tasks may not be assigned, incorrect utilities may be communicated
and, in general, sub-optimal solutions reached.  Furthermore, the
requirement that the agents themselves determine the cost of their
actions assumes that they have the computational capability to do
so. Furthermore, the bids placed by each agent need to be a strong
representation of their capability to perform a task which may be hard
to estimate without expert knowledge. However, market based methods
are well suited to explanation through argumentation (similar to
\cite{Jung2001DistributedArgumentation}.

\fr{The game-theoretic approaches described above might suffer from the
  same drawbacks identified above for fault detection, namely reliance
  on communication and on a single central authority. I'd rather
  favour distributed approaches. Also, market-based mechanisms and
  negotiation might lead us to a completely different direction.}

@@

There has also been some interesting work in probabilistic
verification of market based approaches.  Most notable to me is
\cite{Pallottino2007ProbabilisticAvoidance} which considers the case
of conflict avoidance. Though their method focuses on collision
avoidance, it highlights the need for verification of conflict
resolution and goal achievement in market based approaches with
different payoff structures. Sirigineedi et
al. \cite{Sirigineedi2010DecentralisedApproach} make a step in this
direction by considering the verification of cooperative surveillance
along a route network.  From my understanding, this means that they
were able to verify that their agents were able to traverse along the
network without interference. However, this, as always, requires
further analysis to truly understand.

\subsection{Directions}

The particular considerations which have jumped out to me from the above analysis are as follows:

\begin{enumerate} 
	\item Verification of goal achievement under different payoffs: can we ensure that
	self-interested agents will, in fact, show cooperative emergent properties? A similar question
	arises in terms of valuations (how much cost each agent incurs). 
	\item A priori consideration of
	reliability: Can we learn and take into account the fact that robots may fail throughout the
	progress of a mission when we assign tasks? 
\end{enumerate}

\subsection*{Stochastic Games}

\section{Hard Coded}

\section{MARL}

Reinforcement learning extends the Markov Decision Process problem by
considering the case where the payoff model is not known. This, of
course, is the case for most real world environments. As such, MARL
algorithms can perhaps be considered to be more applicable than
Dec-POMDP models.
\fr{Why would it be so? after all, also MARL assumes a certain pay-off structure.}

Fortunately, MARL has picked up a lot of traction in
research recently, with a large body dedicated towards solving the
many problems it presents.

The largest problem in MARL is the non-stationarity of the environment \cite{Hernandez-LealA}. In
single-agent settings, it is assumed that the environment is Markovian. However, this must be lifted
in the Multi Agent setting since other agents in the environment will be learning concurrently. This
learning will be based on their own history of interactions which extend beyond the previous state.
As such, we must now consider that the policy for any one agent will depend on the policy of all
other agents. As such, a big concern in this area is regarding convergence guarantees and the
stability of the learner system. Approaches to this will be discussed in the next chapter.

\subsection*{Agent Modelling}

Returning to the problem of non-stationarity, solutions have been presented in which the agent
models the learning of other agents. A noteworthy example of this is found in
\cite{Foerster2018LearningAwareness} in which the agent performs a one-step lookahead of the other
agents' learning and optimises with respect to this expected return. They show that this leads to
stable learning and can even lead to emergent cooperation from competition. However, the method
requires that both agents have exact knowledge of the others' value functions in order to perform
the one step lookahead. Furthermore, it has only been considered for the case of a two agent
adversarial game and so the scalability of the system to multiple agents is not yet understood.
Another method presented by Mao et al. \cite{MaoModellingDDPG} uses a centralised critic to collect
the actions and observations of all agents and allows it to model the joint policy of teammates.
This is shown to generate cooperative behaviour across four agents and so is more applicable to real
world settings. However, its disadvantage over the method presented in
\cite{Foerster2018LearningAwareness} is that the critic is centralised. In real world settings, this
requires the presence of an agent (perhaps a laptop) which is able to handle the computational load
of determining a joint policy across all agents and must then communicate the Q-values of all agents
back to them. This is both a taxing both in terms of computation and time.

Hong et al \cite{Hong2018ASystems} present a similar system for modelling teammate policies by
tasking a CNN with determining the policy features of other agents and then embedding these as
features in its own DQN. This shows strong performance in settings where other agents dynamically
change their policies. The concerns with this, however, are that, as the number of agents in the
field increase, the CNN in each agent must perform another approximation. This places strong
requirements on the performance of the CNN since errors in estimation will accumulate as the number
of agents increases. Similarly, the complexity of the DQN will increase as more feature vectors are
added.

Finally, all of the above methods are not robust to evolving numbers of agents. The problem of agent
modelling is an important one to ensure stable learning and to understand the evolution of the
system. It also presents a strong challenge and is open to exploration. To put it in context the
methods described in this section are all from 2018-19, so its all very new.

\subsection{Directions}

I still have a lot of reading to do regarding MARL, which, in turn, will identify new directions.
However, on initial assessment I put forward

\begin{enumerate} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
the stability of the learning process. However, the particular problem I suggest is to consider the
modelling in a decentralised manner and with the consideration of evolving numbers of agents in
teams. \end{enumerate}

\fr{This looks like an interesting, non-trivial problem: how can we
  represent the other agents within the agent model itself, in order
  to improve learning in MARL? Shall we have a closer look at this problem?}

\section{MARL Approaches} \label{sec::MARL Approaches}

The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
policy may be the concatenation of all the individual policy or it may just be options for each
agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
and so, in this section, I will try to consider the broad spectrum of methods which attempt to
achieve this Nash equilibria. I will start with the more foundational methods which are, thankfully,
all reviewed by Schwartz in  \cite{SchwartzMulti-agentApproach}. I will use the chapters of the book
to help guide this review. I am not referencing the individual papers immediately, though the
references can be found in the book.

\subsubsection*{Learning in Two Player Matrix Games}

The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
method of linear programming (in which constraints are linear). This will be important in
considering more current methods. A similar consideration is given to the infinitesimal gradient
ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
particular problem in games where there are multiple Nash equilibria. However, in practice it is
difficult to choose a convergence rate of the step size and, without an appropriate choice the
strategy may oscillate as shown in the book. To address this, a modified approach is presented by
Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
payoff matrix (which is not so much of a problem for model based methods) and the opponent's
strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
players with minimal oscillation.

The above methods are all centralised techniques, in which a controller determines the optimal joint
policy for both agents. However, in real scenarios it is often preferable that each agent learns
their own strategy, a task which must be completed without information of the other agent's
strategy. The methods presented towards this problem are: linear reward-inaction ($L_{R-I}$) which
guarantees convergence to NEs in games which contain pure NEs, linear reward-penalty ($L_{R-P}$)
which can guarantee convergence to mixed strategies given the appropriate parameters, lagging anchor
algorithm which also converges to mixed strategies, and the author's own proposal of the $L_{R-I}$
lagging anchor algorithm which can converge to both pure and mixed NEs.

\subsubsection*{Learning in Multiplayer Stochastic Games}

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz
considers two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
shortly. Schwarz then presents a review of MARL methods (as of
September 2014)

\fr{All the above looks extremely interesting. I would explore the
  above for decentralized and partially observable settings. What
  results are mentioned \cite{SchwartzMulti-agentApproach} under such
  assumptions?}

\subsection*{Dec-POMDP and MARL}

As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
The methods which I feel may be applicable are  \begin{enumerate} \item Alternating Maximisation: This
is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
order to make this work, we would also need to consider how to select the feature space of sub-trees
and how to collect this information. \end{enumerate}

\chapter{Multi Agent Control}

\section{Stochastic and Robust Model Predictive Control}

The idea of Stochastic Control is best described in the research statement of the Control and
Analysis of Stochastic Systems (CASS) group at Penn State:

\begin{displayquote}
	"...to model, predict and control uncertain engineering systems where the interplay between
	dynamics and uncertainty (stochasticity) is important."
\end{displayquote}

When operating in the real world, systems are subject to uncertainty and environment perturbations.
Despite this, for their safe operation, they must provide certain guarantees (such as collision
avoidance) and remain stable. It is with this in mind that we must design control mechanisms for the
system which satisfy these requirements, even in the face of uncertainty. Methods in stochastic
control have found their way into controlling power distribution, chemical processes and (of course)
robotics.

\subsection*{Model Predictive Control}

Model Predictive Control is a long standing paradigm in AI which looks specifically at the problem
of operating real-world agents safely in the face of environmental disturbances. The overarching
idea begins with the assumpion that we have a model of the environment. As an example, in
the case of autonomous vehicles, we have a model of how adjusting the angle of the front wheels will
affect the heading of the car. We then perform a finite horizon look ahead, in which we estimate the
environment state for a few time steps ahead, and generate a policy for this horizon. The agent
performs the immediate action generated by the policy, and then we repeat the process, after taking
measurements of the environment to determine the error in the system. Throughout this process, the
controller (a.k.a. policy) must remain stable, but also satisfy constraints. From our previous
example, a likely constraint would be that the controller will never result in the car going on the
pavement, where it would present a real hazard to pedestrians. It is through these constraints, and
the requirement of stability that the system is required to remain safe throughout operation. To
that end, mathematical proofs of these properties are provided in the literature ensuring that we
can trust in the system's performance.

Deterministic MPC assumes that the environment is completely deterministic and, therefore, assumes
knowledge of the exact nature of the disturbances. This somewhat naive assumption simplifies
computation and so appears often in the literature, as in \cite{Rosolia2018}. However, it does not
provide strong guarantees outside of games and simulations. Robust MPC brings this to a higher level
of abstraction in which system perturbations, though deterministic, lie on a bounded set. Therefore,
we no longer assume the exact nature of the environment and can guard against worst case scenarios.
This is extremely effective in closed environments or for simple tasks, but falters in more complex
environments.

Stochastic Model Predictive Control (SMPC) lifts the assumption made in MPC, namely that
perturbations are deterministic and lie on a bounded set \cite{Mesbah2016}. To accomplish this, we
define chance constraints, for which probabilistic guarantees must be determined. Furthermore,
optimality is defined in terms of the minimisation of the expectation of a probabilistic
cost function. This formulation brings about controllers which are more applicable and robust when
deployed. However, the field is in its infancy and presents a number of theoretical challenges.
These are best described by Mesbah in \cite{Mesbah2016}

\begin{enumerate}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{enumerate}

Since the review \cite{Mesbah2016} was written in 2016, there have been a number of approaches
towards solving some of these problems, most notably the intractability of the chance contraints.
For instance, in  \cite{Paulson2019}, Paulson and Mesbah propose the use of joint chance constraints
in considering time varying stochastic disturbances as well as model uncertainty. This is shown to
be strongly suited to non-linear systems, which itself is an open problem in the MPC sphere.

The research in using Distributed Predictive Control is quite sparse as compared with, for example,
single agent predictive control. The added complexity of stochastic environments has meant that this
area of research is still very open for looking into. With this said, the main works that I have
found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
Usually these are some combination of the following:

\begin{enumerate}
	\item The agents act in a deterministic environment. This suggests that predicted futures will
	be close enough to the ground truth.
	\item The agents are uncoupled from one another. This is a strong assumption to make and
	essentially allows us to consider the agents as completely independent of one another. 
	\item The agents can easily communicate with one another. This allows for longer pieces of
	communication (most often predicted trajectories) to be communicated between agents.
\end{enumerate}

\subsection{Directions}

The problem of MPC, both in the stochastic, and the robust sense, are rife for work in theoretical
and applied problems. Control in autonomous systems is also one of the more applicable problems
related to STAI since it requires that we place mathematical guarantees on the performance and
stability of the system as well as guarantees on the satisfaction of constraints. This is, of
course, an ever present problem in autonomous systems which operate in the real world. I begin by
listing the more theoretical areas for exploration in MPC before then considering their application
domains.

\begin{enumerate}
	\item Significant exploration is required with regards to the optimisation problem. Especially
	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
	approximate methods (such as sampling) should be explored and their effect on the system
	guarantees presented.
	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
	determine the uncertainty in the environment model in order to generate control laws. We should
	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
	particle filters, against modern deep learning methods for propagation.
	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
	together whilst maintaining a specified distance from one another). Consider, then, the case
	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
	and hence requires adaptation. It would again be interesting to consider the use of neural
	networks in this manner. However, specifically we should consider whether the use of a function
	approximator in the form of an NN might result in a violation of the constraints.
	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
	effect that each agent has on the other, the effect of the environment on all agents, estimating the
	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
	here that I believe game-theoretic notions (especially differential games) will come to our
	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
	in the case of multiple disturbances, but I will elaborate on this in the applied problems
	section.
\end{enumerate}

the following presents a consideration of the applied end of MPC problems. I have tried to focus on
the domain independent suggestions, since the domain specific ones are virtually limitless.

\begin{enumerate}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
	\item Modular Robotics?
\end{enumerate}

\fr{All the above looks interesting. However, we need to understand
  how much the scalability issue is going to affect the strength of
  the results we can expect. Is a multi-agent extension of MPC
  completely hopeless? or can we find ``islands of tractability'',
  perhaps in combination with some of the other methods that you
  mention?}

\section*{Multi Agent Dynamics}

Multi Agent Dynamics considers the problem of mathematically modelling learning in Multi Agent
Systems (MAS). This model then serves to be able to predict the evolution of a learning system as
well as to understand the trajectory of learning. Typically, this looks at considering whether or
not the method is likely to converge towards a Nash equilibrium. This is generally a difficult
problem to solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this
applicability into real world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world
environments.

\section{Stability of Learning Agents}

Stability may be looked at from the view point of two perspectives. The first is from an
optimisation point of view. This considers the dynamics of the learning model, allowing us to better
choose our parameters and design our models so that they may converge to a stable result. The second
is from the view point of the state-action space of a learnt model. This allows us to determine,
before the MAS is deployed, which set of state-action pairs will lead to unstable behaviour. This
knowledge allows us to consider which state-action pairs should be avoided. In both cases, stability
analysis allows us to build multi agent systems which will learn and act in the way that we expect
them to.

In \cite{Letcher2019DifferentiableMechanics}, Letcher et al. model gradient descent learning of
generative-adversarial-networks (GANs) as a two-player differentiable game. A differentiable game is
one in which the loss function is twice differentiable. Using this formulation, they are able to
analyse the system from new perspectives by considering the current state-of-the-art understanding
of differentiable game theory. Whilst, at first glance, this may seem like a purely theoretical
exercise, they go on to show that the insights gained allow them to develop a new multi-objective
optimisation technique for GANs which shows stronger convergence properties, most notably of which
is that it guarantees that the method finds a stable equilibrium (and avoids saddles) between the
two players' loss functions.

Jin and Lavaei \cite{Jin2018Stability-certifiedPerspective} consider the policy of a reinforcement
learning agent as a non-linear, time varying feedback controller. Using this notion, they then
consider the bounded-input-bounded-output stability of the system. They do this by analysing the
ratio between the total output and total input energy (called the L2 gain). If the L2 gain remains
finite then the system may be considered to be stable. They then apply these considerations on
real-world applications including multi-agent flight formation and obtain stability certificates
(essentially confirming that the system will remain stable under certain conditions) for the learned
controller.

>>>>

Game Theory has a rich history when considering an understanding of multi-agent systems. These begin
in economics but have found a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of the categories in this section
(although its synergy with swarms is requires significant development) since Dec-POMDP and MARL
methods have both used game theory to support their frameworks. In fact, Dec-POMDP is a subset of
Partially Observed Stochastic Games (POSG), in which all agents use the same payoff.

\section{Market Based Methods}

@@

Whilst there are different variants to auctioning, the general procedure is that an auctioneer who
has knowledge of a task (or multiple tasks) will set up an auction for said task. Agents can then
make bids on these tasks and, once the auction is complete, the highest bid will win the task. In
the specific application to robotics, a robot's bid will often reflect the costs, suitability or
utility their undertaking the task \cite{BernardineDias2006Market-basedAnalysis}. This immediately
highlights a few points. The first is that the method is not too heavily reliant upon a single
processor to determine some joint policy. Tasks are allocated on a case-by-case basis and the
utilities are calculated by the agent themselves. The only centralised process is the auctioneer's
assessment of the winner which then relays this information back to them. The downside of this is
that the system is heavily reliant upon strong communication channels, without which tasks may not
be assigned, incorrect utilities may be communicated and, in general, sub-optimal solutions reached.
 Furthermore, the requirement that the agents themselves determine the cost of their actions assumes
that they have the computational capability to do so. Furthermore, the bids placed by each agent
need to be a strong representation of their capability to perform a task which may be hard to
estimate without expert knowledge. However, market based methods are well suited to explanation
through argumentation (similar to \cite{Jung2001DistributedArgumentation}.

@@

There has also been some interesting work in probabilistic verification of market based approaches. 
Most notable to me is \cite{Pallottino2007ProbabilisticAvoidance} which considers the case of
conflict avoidance. Though their method focuses on collision avoidance, it highlights the need for
verification of conflict resolution and goal achievement in market based approaches with different
payoff structures. Sirigineedi et al. \cite{Sirigineedi2010DecentralisedApproach} make a step in
this direction by considering the verification of cooperative surveillance along a route network. 
From my understanding, this means that they were able to verify that their agents were able to
traverse along the network without interference.

\section{Stochastic Games}

\TODO{For the love of God do this already}

\section{Game Theoretic Control}

Game theory can often be applied to problems of control theory (particularly where there are
multiple agents) to develop robust controllers which guarantee properties of stability and
constraint satisfaction.

This idea is explored in \cite{Marden2018AnnualControl}. Here, a zero-sum game is considered in
which the players are a controller and an adversarial environment. The design of the controller must
be such that it is able to drive the system to zero error. To illustrate, consider the problem of
designing a controller for a re-entry vehicle, as in \cite{Breitner1994ReentryGame}, in which
vortices seek to destabilise the agent. This will allow us to build stable agents in a much more
efficient manner since we can simulate the adversarial environment and hypothetical scenarios the
agent may encounter without actually encountering them. The same notion is explored by Bardi et al
\cite{Bardi1991DifferentialDisturbances}.

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
avoidance problem, similarly from the point of view of differential game theory. They develop a
robust feedback system for the robots which they show to be able to drive the system towards
predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own payoff structure and have
limited communication with one another. The author shows that an approximate equilibrium can be
found using algebraic methods and illustrate the capabilities of the technique using a collision
avoidance example. For the sake of brevity, I will not include all of the numerous strides that
Mylvaganam has introduced to the area. However, I must conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
games, including linear-quadratic differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
induced across the players (a notion was suggested in the research proposal) and mean-field games,
which is discussed in 'MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the Nash equilibria are
admissable iff they are locally exponentially stable (which the author often shows with the aid of
Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
calculate online. The author then shows that this is not simply a theoretical exercise by applying
the novel methods towards multi-agent collision problems and designs dynamic control laws which
guarantee that each agent will reach their desired state whilst avoiding collision with the other
agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
robot system.
